Paper figures

### 2020-12-21 notebooks/poster_plots_1023.Rmd
notebooks with all analyses i have until Dec 21st 2020

random_dfs_list = lapply(list.files('data/interim/pcc_1020/random_dfs', full.names=T), data.table::fread)
random_dfs_list = mapply(c, random_dfs_list, list.files('data/interim/pcc_1020/random_dfs'), SIMPLIFY=F)
random_dfs_100 = data.table::rbindlist(random_dfs_list,fill=T)
colnames(random_dfs_100)[length(colnames(random_dfs_100))] <- 'filename'
```
```{r}
theme_fontsize = theme(axis.text = element_text(size = 14), axis.title = element_text(size = 20), legend.text = element_text(size=16))
```

@@

degree_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     combined_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     combined_df%>%filter(group=='random'),aes(x=deg,y=..scaled..,color=group),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize
eff_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= combined_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize+
annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
sensitivity_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= combined_df%>%filter(group=='random'),
               aes(x=sens_norm ,y=..scaled..,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())+
theme_fontsize+
annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
dens_lgn = cowplot::get_legend(sensitivity_dens)
dens_plots = cowplot::plot_grid(degree_dens+theme(legend.position='none'), eff_dens+theme(legend.position='none'), sensitivity_dens+theme(legend.position='none'), ncol=3,labels=c('A','B','C'))
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
#ggsave('tmp.png')
#ggsave('reports/figures/poster_figures_1023/fig3.png')
#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)

>>>>

random_dfs_list = lapply(list.files('data/interim/pcc_1020/random_dfs', full.names=T), data.table::fread)
random_dfs_list = mapply(c, random_dfs_list, list.files('data/interim/pcc_1020/random_dfs'), SIMPLIFY=F)
random_dfs_100 = data.table::rbindlist(random_dfs_list,fill=T)
colnames(random_dfs_100)[length(colnames(random_dfs_100))] <- 'filename'
random_dfs_100<- random_dfs_100%>%mutate(eff_norm = eff/nrow(pcc_df), sens_norm=sens/nrow(pcc_df))
```
```{r}
theme_fontsize = theme(axis.text = element_text(size = 14), axis.title = element_text(size = 20), legend.text = element_text(size=16))
```

@@

degree_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     combined_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     random_dfs_100%>%dplyr::mutate(group='random'),aes(x=deg,y=..scaled..,fill=filename),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize
eff_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= random_dfs_100%>%mutate(group='random'),
               aes(x=eff_norm ,y=..scaled..,fill=filename),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize+
annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
sensitivity_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= random_dfs_100%>%dplyr::mutate(group='random'),
               aes(x=sens_norm,y=..scaled..,fill=filename),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())+
theme_fontsize+
annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
dens_lgn = cowplot::get_legend(sensitivity_dens)
dens_plots = cowplot::plot_grid(degree_dens+theme(legend.position='none'), eff_dens+theme(legend.position='none'), sensitivity_dens+theme(legend.position='none'), ncol=3,labels=c('A','B','C'))
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('tmp.png')
#ggsave('reports/figures/poster_figures_1023/fig3.png')
#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)
